\documentstyle{letter}
\begin{document}
\signature{Walter Askew\\
  1745 Orrington Avenue\\
  Apartment 2N\\
  Evanston, IL 60201}

\begin{letter}{Mr. Francesco Pinto\\
    CEO Defyned Interactive}

  \opening{Dear Mr. Pinto,}
  
  I would be very interested in a developer position at Defyned
  Interactive on the Chatyeo project.
  I graduated from Emory University in Atlanta this May where I
  studied Comparative Literature, Computer Science and Linguistics.
  I have practical programming experience from a few different jobs,
  as well as research experience in the Natural Language Processing
  field.
  The Chatyeo project seems like a very good fit for my interests and
  talents.

  In college, I discovered that the intersection of my interest in
  literature and programming is Linguistics and the Natural Language
  Processing field.
  I began taking a few Linguistics courses, and I became a research
  assistant with a professor who worked in NLP.
  Chatyeo's aim to mine information from users' conversations bears a
  resemblance to my Honors Thesis project.
  My Honors Thesis describes an attempt I made to mine relevant
  medical knowledge from web forums for disease sufferers.
  Like the Chatyeo project, my Honors Thesis mines conversations to
  create a knowledge base that the users are not even directly aware
  they are creating.
  I think these sort of projects are interesting because they draw out
  the knowledge that sits implicitly behind the words a users has
  typed into an application.
  I find Linguistics a fascinating field, and I have been very happy
  to discover how much opportunity there is for me to combine my
  interest in language with my enjoyment of programming.

  I would be grateful for an opportunity to pursue employment with
  Defyned Interactive.
  I am available for interviews at any day or time, as I am
  currently unemployed.

  \closing{Thank you for the opportunity,}
\end{letter}
\end{document}