\documentstyle{letter}
\begin{document}
\signature{Walter Askew\\
1341 N Campbell\\
Chicago, IL 60622}

\begin{letter}{}


\opening{Dear Mr. Rosenberg,}
  
I am very interested in pursuing a position as a
developer at Food Genius Inc.
I have a strong interest in Linguistics, Natural Language
Processing and data mining, and I would be very excited for an
opportunity to pursue these interests professionally.

While working on my Computer Science and Comparative Literature
degrees in college, I became interested in pursuing their intersections
in Linguistics and NLP.
I applied for a job as a research assistant, and I soon found myself
working on the most interesting problems I had ever encountered. 
I worked with my professor and several other graduate students on data
mining, machine learning and statistical NLP projects.
One project had us attempting to diagnose patients using doctors'
triage reports, while another had us trying to identify whether a
given hypothesis could be inferred from a set of statements.
I worked with the same professor on my honors thesis, which describes
an attempt to compute useful medical information by mining textual
sources such as  web forums and medical journals.
This experience seems particularly relevant to a position at Food
Genius, as the focus of my thesis was in mining user-generated textual
data. 

My time as a research assistant was wonderfully interesting and
challenging, and I have wished to pursue similar work ever since.
I am confident that my time spent performing NLP research as a student
has provided me with a solid foundation in the field, while my
professional development as a Python programmer has cemented the
practical programming skills I need to build robust implementations of
NLP and data mining systems. 

I would be grateful for a chance to continue pursuing my interests in
Natural Language Processing and data mining.  
I believe that working at Food Genius would allow me to pursue
solutions to interesting and challenging problems, and I would
appreciate the chance to interview for a position as a developer.

\closing{Thank you for the opportunity,}
\end{letter}
\end{document}
