\documentstyle{letter}
\begin{document}
\signature{Walter Askew\\
  2065 N Hoyne Ave\\
  Apartment 2R\\
  Chicago, IL 60647}

\begin{letter}{}

  \opening{To Whom it May Concern,}
  
  I would be very interested in pursuing a position as a Python
  developer at JuJu.
  I graduated from Emory University in Atlanta this past May where I
  studied Comparative Literature, Computer Science and Linguistics.
  I have practical programming experience from a few different jobs,
  as well as research experience in the Natural Language Processing
  field.
  I became interested in JuJu after seeing the post on the Python Job
  Board which encouraged developers interested in machine learning and
  text search to apply.

  I believe I would be a good fit at JuJu because I enjoy programming
  in Python, and because I would be very excited to continue to work on
  NLP and machine learning problems.
  In college, I discovered that the intersection of my interests in
  literature and programming is Linguistics and the Natural Language
  Processing field.
  I began taking a few Linguistics courses, and I became a research
  assistant with a professor who works in the NLP field.
  The work I did with him and other grad students involved data
  mining, machine learning and statistical NLP.
  My Honors Thesis is an example of work which could serve as a
  valuable background for work at JuJu.
  My thesis describes an attempt to compute useful medical
  information by mining textual sources such as  web forums and
  medical journals.
  The project involved mining large textual corpora and applying
  supervised machine learning to compile relevant medical knowledge.
  My other work in the NLP field includes writing a publication with a
  Graduate student which applies machine learning techniques towards
  the problem of recognizing textual entailment.

  I would be grateful for an opportunity to pursue employment with
  JuJu, and I would appreciate the chance for an interview.  If
  requested, I would be happy to provide copies of my honor's thesis
  and my publication.

  \closing{Thank you for the opportunity,}
\end{letter}
\end{document}