\documentstyle{letter}
\begin{document}
\signature{Walter Askew\\
1220 N Washtenaw Apt 3R\\
Chicago, IL 60622}

\begin{letter}{}

\opening{To Whom It May Concern,}

I would be very excited to use my experience architecting and building
scalable systems to accelerate learning for kids.
I have designed and built systems for large-scale aggregation of news
headlines and deployed public-facing web applications, and I would
enjoy the opportunity to continue building exciting technology
stacks.
Designing and building quality software is something I am passionate
about.
A look through my open source work on GitHub for Freedom Games reveals
a well-documented code base with 99 percent unit test coverage.
I am a strong believer in test driven development, readable code and
good documentation.

One of the things that most excites me about working at mSchool is the
ability to improve education opportunities for children.
Outside of work, I have enjoyed being involved in education in a
variety of ways,
from teaching ceramics classes to volunteering as a Math tutor.
I would be very excited to bring my interests in software engineering
and teaching together while building a brighter future in education
for youth.

Moving to New Orleans is also something I've been thinking about
ever since my last visit.
I would be very happy to join you in the best city in the world,
especially after this last winter in Chicago.
It would be wonderful to speak to you about using my background in
system architecture and software engineering to help students achieve
their learning goals.

\closing{Thank you for the opportunity,}
\end{letter}
\end{document}
