\documentstyle{letter}
\begin{document}
\signature{Walter Askew\\
  2065 N Hoyne Ave Apt 2R\\
  Chicago, IL 60647}

\begin{letter}{To Whom it May Concern}

\opening{}

   I would be very interested in attaining a position as developor for
   your reserach team. 
  I graduated from Emory University in Atlanta this May where I
  studied Comparative Literature, Computer Science and Linguistics.
  I have practical programming experience from a few different jobs,
  as well as research experience in the Natural Language Processing
  field.
  I am interested in the position primarily because I enjoyed my
  experience as a research assistant during my college career.

  I believe I would be a good fit for the position because I am
  enthusiastically interested in open source software and research.
  One of the most rewarding aspects of my college carreer was my
  participation in research for the Compter Science department.
  I enjoyed my time as a research assistant at Emory because I was able to
  leverage my programming skills in an academic setting.
  I consider myself an intellectually interested person, and I was
  excited to be able to contribute to the creation of knowledge and
  advancement of science.
  I also found research to be an enjoyable application for programming
  due to the forensic nature of research.
  I enjoyed participating in discussions
  regarding how computation could be useful in answering research
  questions as well as writing the programs themselves.
  While I don't have experience with Ruby on Rails, I do have
  experience with similair technologies as well as an interest in
  learning and working with new open source software.

  I would be grateful for an opportunity to pursue employment with
  your research team.
  I would appreciate a chance for an interview, and I can make myself
  available for discussion anytime outside of my work hours.


  \closing{Thank you for the opportunity,}
\end{letter}
\end{document}