\documentclass{letter}
\usepackage[
  colorlinks = true,
  linkcolor = blue,
  urlcolor  = blue,
  citecolor = blue,
  anchorcolor = blue]{hyperref}

\begin{document}

\signature{Walter Askew\\
1221 Washtenaw Apt 3R\\
Chicago, IL 60622}

\begin{letter}{}

\opening{To Whom it May Concern,}

I have strong interests in Linguistics, Natural Language
Processing and machine learning, and I would be very excited for an
opportunity to pursue these interests professionally.
I have been writing Python professionally for five years, but have not
had a chance to apply my interests in NLP since working as an
undergraduate researcher.
Being able to return to my interests in NLP and machine learning would
be a very exciting change for me.

While working on my Computer Science and Comparative Literature
degrees in college, I became interested in pursuing their intersections
in Linguistics and NLP.
I applied for a job as a research assistant, and I soon found myself
working on the most interesting problems I had ever encountered.
I worked with my professor and several other graduate students on data
mining, machine learning and statistical NLP projects.
One project had us attempting to diagnose patients using doctors'
triage reports, while another had us trying to identify whether a
given hypothesis could be inferred from given a set of statements.
I worked with the same professor on my honors thesis, which describes
an attempt to compute useful medical information by mining textual
sources such as web forums and medical journals.

Since college, I have cemented my skills as a programmer working at
fast-paced software companies.
My most recent work is available on GitHub at the following URL:

\href{https://github.com/freedomgames/Planet-Lab}
     {https://github.com/freedomgames/Planet-Lab}

The code in the `backend' directory is for a fairly simple REST
service written in Python and the Flask framework.
Though serving relatively simple needs, the code itself is
thoroughly unit tested, documented and cleanly written.

I would be grateful for a chance to continue pursuing my interests in
NLP and machine learning.
I believe that working at Scrapinghub would allow me to pursue
solutions to interesting and challenging problems, and I would
appreciate the chance to interview for a position as a developer.

\closing{Thank you for the opportunity,}
\end{letter}
\end{document}
