\documentclass{letter}

\begin{document}

\signature{Walter Askew\\
1221 Washtenaw Apt 3R\\
Chicago, IL 60622}

\begin{letter}{}

\opening{To Whom it May Concern,}

I would be very excited to explore new tools and languages while
investigating the patterns of badly behaving software.
I've only written Python professionally, but having played with
languages like Haskell in my free time I find myself very interested
in expanding into the world of functional programming vocationally.
My college background in machine learning is something I would love to
resurrect and apply towards tasks as interesting as classifying
behaviors of programs.

As an undergraduate researcher, I worked with my professor and several
other graduate students on data mining, machine learning and
statistical NLP projects.
Although I've yet to find a professional outlet for this work, I
remember these problems as some of the most interesting I've ever
worked on.
One project had us attempting to diagnose patients using doctors'
triage reports, another had us trying to identify whether a
given hypothesis could be inferred from given a set of statements, and
my honor's thesis describes an attempt to classify diseases'
likelihood of comorbidity by mining textual sources such as web forums
and medical journals.
I would love to return to classification problems professionally after
enjoying working on them so much as a college student.

I would also be happy to join another talented team of engineers.
Having previously worked with one of your current employees at
Narrative Science, I know how pleasant it is to be surrounded by
bright engineers.
Working remotely is also something I would like to return to.
One thing I appreciated while working remotely for SteepRock was how
it naturally seemed to shift company culture away from politics and
towards no-nonsense work.
I would be very happy to interview for a position working with
talented engineers on interesting problems in a language as
fun as Lisp.

\closing{Thank you for the opportunity,}
\end{letter}
\end{document}
